\documentclass[12pt]{article}

\usepackage[letterpaper,margin=1in]{geometry}

\setlength{\parindent}{0pt}

\usepackage{amssymb}
\usepackage{amsmath}

\newcommand{\assessmentTitle}{
  Standard Assessment 1
}

\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}% Default \headrulewidth is 0.4pt
\renewcommand{\footrulewidth}{0pt}% Default \footrulewidth is 0pt
\chead{\footnotesize\bf\assessmentTitle}
\cfoot{\small Page \thepage}

\newcommand{\makeHeader}[4]{
\thispagestyle{empty}
\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
#1 | #2 | #3 | #4
}}}
\end{center}
\vspace{0.1in}
\makebox[\textwidth]{
  Name:\enspace\hrulefill\hrulefill\hrulefill
}
}

\usepackage{xcolor}

\newcommand{\standardQuestion}[2]{
\newpage
\begin{center}
  \begin{tabular}{|l|c|}
  \hline
    \parbox{5in}{
      \textbf{#1}: This student is able to...\\
      #2
    }
  &
    \parbox{1in}{
      \vspace{0.1in}
      \footnotesize \textcolor{gray}{Mark:}
      \vspace{0.7in}

      \tiny \textcolor{gray}{(Instructor Use Only)}
    }
  \\\hline
  \end{tabular}
\end{center}
}

\newcommand{\csch}{\operatorname{csch}}
\newcommand{\sech}{\operatorname{sech}}



\begin{document}

\makeHeader{
MA 126 }{ Spring 2017 }{ Prof. Clontz }{ \assessmentTitle
}

\begin{itemize}
  \item Each question is prefaced with a Standard for this course.
  \item When grading, each response will be marked as follows:
  \begin{itemize}
    \item \(\checkmark\):
      The response is demonstrates complete understanding of the Standard.
    \item \(\star\):
      The response may indicate full understanding of the Standard, but
      clarification or minor corrections are required.
    \item \(\times\):
      The response does not demonstrate complete understanding of the Standard.
  \end{itemize}
  \item Only responses marked with a \(\checkmark\) mark count toward your
    grade for the semester.
    Visit the course website for more information on how to improve
    \(\star\) and \(\times\) marks.
  \item This Assessment is due after 50 minutes. All blank responses will
    be marked with \(\times\).
\end{itemize}





\standardQuestion{C01}{
  Derive properties of the logarithmic and exponential functions from their definitions.
}

Use the definition \(\ln x = \int_1^x \frac{1}{t}\,dt\) to prove that
\(\ln(x/a)=\ln x - \ln a\) for all positive real numbers \(x\) and \(a\).





\standardQuestion{C02}{
  Prove hyperbolic function identities.
}

Use the definitions
\[
  \sinh(x) = \frac{e^x-e^{-x}}{2},
  \cosh(x) = \frac{e^x+e^{-x}}{2}
\]
to prove the following identity.
\[
  \cosh^2(x) = 1+\sinh^2(x)
\]




\standardQuestion{S01}{
  Find derivatives and integrals involving logrithmic and exponential functions.
}

a) Find \(\frac{d}{dy}[\ln(y^2+1)+e^{3y}]\).

\vspace{3in}

b) Find \(\displaystyle\int\left(\frac{e}{x}+e^x\right)\,dx\).




\standardQuestion{S02}{
  Find derivatives and integrals involving hypberbolic functions.
}

a) Find \(\frac{d}{dx}[\cosh(2x-7)+\sinh(x^2)\csch(x^2)]\).

\vspace{3in}

b) Find \(\displaystyle\int 5\sech(t)\tanh(t)\,dt\).








\newpage

\textcolor{gray}{Use this space if you need extra room for a problem:}

\end{document}
