\documentclass[12pt]{article}

\usepackage[letterpaper,margin=1in]{geometry}

\setlength{\parindent}{0pt}

\usepackage{amssymb}
\usepackage{amsmath}

\usepackage{multicol}

\newcommand{\assessmentTitle}{
  Standard Assessment 5
}

\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}% Default \headrulewidth is 0.4pt
\renewcommand{\footrulewidth}{0pt}% Default \footrulewidth is 0pt
\chead{\footnotesize\bf\assessmentTitle}
\cfoot{\small Page \thepage}

\newcommand{\makeHeader}[4]{
\thispagestyle{empty}
\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
#1 | #2 | #3 | #4
}}}
\end{center}
\vspace{0.1in}
\makebox[\textwidth]{
  Name:\enspace\hrulefill\hrulefill\hrulefill
}
}

\usepackage{xcolor}

\newcommand{\standardQuestion}[2]{
\newpage
\begin{center}
  \begin{tabular}{|l|c|c|}
  \hline
    \parbox{4in}{
      \textbf{#1}: This student is able to...\\
      #2
    }
  &
    \parbox{1in}{
      \vspace{0.1in}
      \footnotesize \textcolor{gray}{Mark:}
      \vspace{0.7in}

      \tiny \textcolor{gray}{(Instructor Use Only)}
    }
  &
    \parbox{1in}{
      \vspace{0.1in}
      \footnotesize \textcolor{gray}{Reattempt/ Correction:}
      \vspace{0.53in}

      \tiny \textcolor{gray}{(Instructor Use Only)}
    }
  \\\hline
  \end{tabular}
\end{center}
}

\newcommand{\csch}{\operatorname{csch}}
\newcommand{\sech}{\operatorname{sech}}



\begin{document}

\makeHeader{
MA 126 }{ Spring 2017 }{ Prof. Clontz }{ \assessmentTitle
}

\begin{itemize}
  \item Each question is prefaced with a Standard for this course.
  \item When grading, each response will be marked as follows:
  \begin{itemize}
    \item \(\checkmark\):
      The response is demonstrates complete understanding of the Standard.
    \item \(\star\):
      The response may indicate full understanding of the Standard, but
      clarification or minor corrections are required.
    \item \(\times\):
      The response does not demonstrate complete understanding of the Standard.
  \end{itemize}
  \item Only responses marked with a \(\checkmark\) mark count toward your
    grade for the semester.
    Visit the course website for more information on how to improve
    \(\star\) and \(\times\) marks.
  \item This Assessment is due after 50 minutes. All blank responses will
    be marked with \(\times\).
\end{itemize}





% \standardQuestion{C01}{
%   Derive properties of the logarithmic and exponential functions from their definitions.
% }
%
% Let \(f^\leftarrow\) denote the inverse function of an invertable function
% \(f\); in particular, if \(f(x)=\ln(x)\), then \(f^\leftarrow(x)=\exp(x)\).
%
% Use the theorem
% \(\frac{d}{dx}[f^\leftarrow(x)]=\frac{1}{f'(f^\leftarrow(x))}\) to prove that
% \(\frac{d}{dx}[\exp x]=\exp x\).
%
%
%
%
%
% \standardQuestion{C02}{
%   Prove hyperbolic function identities.
% }
%
% Use the definitions
% \[
%   \tanh(x) = \frac{e^x-e^{-x}}{e^x+e^{-x}},
%   \sech(x) = \frac{2}{e^x+e^{-x}}
% \]
% to prove the following identity.
% \[
%   1-\tanh^2(x)=\sech^2(x)
% \]



% \standardQuestion{C03}{
%   Use integration by substitution.
% }
%
% Find \(\displaystyle\int \frac{6x^2+14}{x^3+7x-3}\,dx\).



\standardQuestion{C04}{
  Use integration by parts.
}

Find \(\int 3x\cosh(x)\,dx\).



\standardQuestion{C05}{
  Identify and use appropriate integration techniques.
}

Draw lines matching each of the five integrals on the left with
the most appropriate integration technique listed on the right.
Multiple techniques may be technically possible, but choose the technique most
useful to begin integration. Every integral and technique is used exactly
once in the correct answer.

\vspace{1em}

\begin{multicols}{2}
  \begin{itemize}
    \item[] \(\displaystyle\int 8x^3\ln(x^4+7)\,dx\)
    \item[] \(\displaystyle\int 8\sec^3(x)\tan^5(x)\,dx\)
    \item[] \(\displaystyle\int \frac{1+3x}{x^3-x}\,dx\)
    \item[] \(\displaystyle\int 2\sin(x)\cosh(x)\,dx\)
    \item[] \(\displaystyle\int \frac{1}{\sqrt{4x^2+1}}\,dx\)
  \end{itemize}
  \columnbreak
  \begin{itemize}
    \item Integration by Substiution
    \item Method of Partial Fractions
    \item Trigonometric Identities
    \item Trigonometric Substitution
    \item Integration by Parts
  \end{itemize}
\end{multicols}



\standardQuestion{C06}{
  Express an area between curves as a definite integral.
}

Find a definite integral equal to the area between the curves
\(y=3^x\) and \(y=4x+1\).
(Do not solve your integral.)



\standardQuestion{C07}{
  Use the washer or cylindrical shell method to express a volume of
  revolution as a definite integral.
}

Find a definite integral equal to the volume of
the solid of revolution obtained by rotating
the region bounded by \(y=\sqrt{x}\), \(y=0\), and \(x=4\)
around the axis \(x=0\).
(Do not solve your integral.)




\standardQuestion{C08}{
  Express the work done in a system as a definite integral.
}

Find a definite integral equal to the work (in foot-pounds) required to
pull out a \(100\)-foot \(25\)-pound rope that is fully extended into
a well.
(Do not solve your integral.)


\standardQuestion{C09}{
  Parametrize a curve to express an arclength or area as a definite integral.
}

Find a definite integral equal to the portion of the parabola \(x=y^2\)
between the points \((1,1)\) and \((4,-2)\).
(Do not solve your integral.)


\standardQuestion{C10}{
  Use polar coordinates to express an arclength or area as a definite integral.
}

Find a definite integral equal to the area inside the circle \(x^2+y^2=4\)
and above the line \(y=1\).
(Do not solve your integral.)


\standardQuestion{C11}{
  Compute the limit of a convergent sequence.
}

Find \(\displaystyle\lim_{n\to\infty}\frac{\sin(n)+1}{n^2}\).





% \standardQuestion{S01}{
%   Find derivatives and integrals involving logrithmic and exponential functions.
% }
%
% a) Find \(\frac{d}{dz}[\ln(3e^z)]\).
%
% \vfill
%
% b) Find \(\displaystyle\int\left(2e+\frac{3}{y}\right)\,dy\).
%
% \vfill
%
%
%
% \standardQuestion{S02}{
%   Find derivatives and integrals involving hypberbolic functions.
% }
%
% a) Find \(\frac{d}{dv}[4\tanh(3v)-\sinh(v^2)]\).
%
% \vfill
%
% b) Find \(\displaystyle\int(\cosh(x)+2\sinh(x))\,dx\).
%
% \vfill



% \standardQuestion{S03}{
%   Integrate products of trigonometric functions.
% }
%
% Find \(\int2\cos^2(y)\,dy\).
%
%
%
% \standardQuestion{S04}{
%   Use trigonometric substitution.
% }
%
% Find \(\displaystyle\int\frac{z+1}{\sqrt{1-z^2}}\,dz\).
%
%
%
%
% \standardQuestion{S05}{
%   Use partial fractions to integrate rational functions.
% }
%
% a) Complete the following partial fraction expansion:
%
% \[
%   \frac{f(x)}{(x^2+3)^2(x-7)^4}
%     =
%   \frac{\hspace{3em}}{x^2+3}
%     +
%   \frac{\hspace{3em}}{(x^2+3)^2}
%     +
%   \frac{\hspace{3em}}{x-7}
%     +
%   \frac{\hspace{3em}}{(x-7)^2}
%     +
%   \frac{\hspace{3em}}{(x-7)^3}
%     +
%   \frac{\hspace{3em}}{(x-7)^4}
% \]
%
% \vspace{1em}
%
% (Assume the degree of \(f\) is less than \(8\).
% You do NOT need to solve for your constants.)
%
% \vspace{1em}
%
% b) Find \(\displaystyle\int\frac{3x^2-x+2}{(x^2+1)(x-1)}\,dx\).
%
% \vfill




% \standardQuestion{S06}{
%   Use cross-sectioning to express a volume as a definite integral.
% }
%
% Find a definite integral that equals the volume of a solid whose base
% is the triangle with vertices \((0,0)\), \((1,2)\), and \((1,-2)\),
% and whose cross-sections perpindicular to the \(x\)-axis are semicircles
% with diameters on the \(xy\) plane. (Do not solve your integral.)




\standardQuestion{S07}{
  Derive a formula for the volume of a three dimensional solid.
}

Prove that the volume of a cone with radius \(a\) and height \(h\)
is \(V=\frac{1}{3}\pi a^2h\). (Hint: Start by letting \(y=\frac{a}{h}x\)
be the hypotenuse of a right triangle with legs length \(h\) and \(a\).)





\standardQuestion{S08}{
  Parametrize planar curves and sketch parametrized curves.
}

a) Give a parameterization of the line segment with endpoints \((4,3)\)
and \((-1,2)\).

\vfill

b) Sketch the curve parameterized by \(x=4t^2\), \(y=2t\)
for all real numbers \(t\).

\vfill



\standardQuestion{S09}{
  Use parametric equations to find and use tangent slopes.
}

Find the points on the parametric curve defined by \(x=3\sin t\),
\(y=-2\cos t\) for \(0\leq t\leq 2\pi\) that have horizontal tangent lines.



\standardQuestion{S10}{
  Convert and sketch polar and Cartesian coordinates and equations.
}

a) Find a polar coordinate equal to the Cartesian coordinate \((1,-\sqrt 3)\).

\vfill

b) Sketch the polar curve \(r=2\sec\theta\) in the \(xy\) plane.

\vfill



\standardQuestion{S11}{
  Define and use explicit and recursive formulas for sequences.
}

Prove that \(a_0=1\), \(a_{n+1}=3a_n\) is a recursive formula for
the sequence defined explicitly by \(a_n=3^n\).






\newpage

\textcolor{gray}{Use this space if you need extra room for a problem:}

\end{document}
